A Fredholm integral equation approach to computing Stokes eigenvalues in the plane

### 2019-03-12 doc/draft-01-stokes/03analysis2.tex
updating fredholm determinant section

>>>>

We now show how this fact can be used numerically
to estimate the Dirichlet eigenvalues.
Suppose that $M_{k}^{N}$ is a Nystr\"{o}m discretization 
of the operator $-2\cD_{k} - 2\cW$ when the boundary 
$\Gamma$ is discretized with $N$ points. 
Let $f^{N}(k) = \text{det}(I + M_{k}^{N})$
where here $\text{det}$ is the standard matrix determinant.
Note that the discretized matrix also depends on the choice
of quadrature rule used in the Nystr\"{o}m discretization
of the operator.
In~\cite{zhao2015robust}, the authors prove that
for computing the Laplace eigenvalues on regions with 
analytic boundaries, when the integral
operators are discretized using Kress-quadratures,
the determinant of the Nystr\"{o}m discretized operators
at the true eigenvalues converge to $0$ exponentially in $N$.
This combined with the analyticity of $f^{N}(k)$ as a function
of $k$ for fixed $N$ proves that
